Supplement to ``{\mytitle}''

### 2023-01-21 si/si.Rnw
prepared documents for submission to Arxiv

<<echo=FALSE, include=FALSE, message=FALSE>>=
h1_epi_evals <- readRDS("../model1/run_level_3/lee1_epi_evals.rds")
h1_end_evals <- readRDS("../model1/run_level_3/lee1_end_evals.rds")

>>>>

<<calcMod1LeeLikes, echo=FALSE, include=FALSE, message=FALSE>>=
h1_epi_evals <- readRDS("../model1/run_level_3/lee1_epi_evals.rds")
h1_end_evals <- readRDS("../model1/run_level_3/lee1_end_evals.rds")
